Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2018-12-05 paper/ms.tex
More work on Carlyn's paper

Supernovae are classified observationally 
by their light curves and spectra~\citep{minkowski41,bertola64,porterfilippenko87,
wheelerharkness1990conf,Fili97}, with the type Ia designation following from
the absence of H in the spectrum and the presence of a specific Si 
line~\citep{filippenko:optical,hillebrandt.niemeyer:type}. These events
have been associated with C burning under degenerate conditions
for some time~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis},
but discerning the setting(s) of these events is proving difficult
and remains the subject of active research. At present there are three
widely-accpeted scenarios: the {\em single degenerate} scenario,
the {\em double detonation} or {\em sub-Chandrasekhar} scenario, 
the {\em white dwarf merger} or {\em double degenerate} scenario.

@@

The white dwarf merger progentor picture has two white dwarfs 
coming together and subsequently exploding~\citep{webbink84,ibentutukov84}.
This scenario provides an abundance of degenerate fuel, which may explain some 
bright events~\citep{scalzo:2010,Yuan:2010}. White dwarf mergers include
variations on the interaction and include

inspiraling pairs, collisions, violent mergers,
and the ``core-degenerate'' model where the merger takes place in
a common envelope
\citep{raskinetal2009,pakmoretal2011,kashi:2011,pakmoretal2012a,Shenetal12}
Also
see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013}
for additional discussion.

There has been debate over what triggers a WD explosion. One of the
primary ideas is the single degenerate process. During this process
the white dwarf accretes material from a giant companion. Once the
white dwarf reaches the Chandrasekhar limit, the star is consumed
by thermonuclear runaway and explodes. Another idea is the double
degenerate process: two white dwarfs merge to exceed the Chandrasekhar
limit. Hydrogen is not expected to be observed since both stars exhausted
their hydrogen long ago.

@@

Brief discussion of progentors...
ancient history~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis}. The
Single degenerate 
\citep{hoylefowler60,trucam71,whelaniben73,Nomo84}. Alternately, in

Other models
\citep{webbink84,ibentutukov84}, in which two WDs inspiral and merge.

\citet{woosleyweavertaam80,taam80a,taam80b, nomoto80,nomoto82b} subchandra

@@

@@

\section{Methods}
\section{Initial Conditions}

>>>>

Supernovae are classified observationally 
by their light curves and spectra~\citep{minkowski41,bertola64,porterfilippenko87,
wheelerharkness1990conf,Fili97}, with the type Ia designation following from
the absence of H in the spectrum and the presence of a specific Si 
line~\citep{filippenko:optical,hillebrandt.niemeyer:type}. These events
have been associated with C burning under degenerate conditions
for some time~\citep{hoylefowler60,arnett.truran.ea:nucleosynthesis},
but discerning the setting(s) of these events is proving difficult
and remains the subject of active research. At present there are three
widely-accpeted scenarios: the {\em single degenerate} scenario,
the {\em double detonation} or {\em sub-Chandrasekhar} scenario, 
the {\em white dwarf merger} or {\em double degenerate} scenario.
We briefly describe these in the subsection that follows. `
Also see~\citet{hillebrandt.niemeyer:type,howell2011,hillebrandtetal2013,calderetal2013}
for additional discussion.

\subsection{Proposed Progenitor Settings}

@@

The double detionation picture is a variation of the single degenerate picture.
In this case, a white dwarf accretes material from a companion, but rather
than gaining enough mass to approach the Chandrasekhar limit, a detonation
occurs in the accreted layer that subsequently triggers a detonation
in the underlying white dwarf \citet{woosleyweavertaam80,taam80a,taam80b,
nomoto80,nomoto82b}. Early studies indicated that a detonation in an 
accreted He
layer could produce an inwardly propagating
shock that would ignite a detonation in the C-O core and found
that this scenario could work for a wide range of white dwarf
masses, not just the near-Chandrasekhar case \citep{livne90}, hence the
moniker ``sub-Chandrasekhar'' \citep{ww94}. Multidimensional supported the
efficacy of this picture~\citep{livneglasner91, livnearnett95,HoefKhok96,
hoeflichetal96, wigginsfalle97,wigginsetal98,garciasenzbravowoosley99} 
but indicated that uncertainties 
like the initial conditions were found to play a significant role.
on the explosion outcome.

A particular problem was that most models 
included a massive He layer, which leads to 
the unobserved result intermediate and heavy elements synthesized in 
the He detonation in the outer parts of the ejecta~\citep{HoefKhok96, 
hoeflichetal96,finkhillebrandtroepke2007,simetal2010}.
\citet{bildstenetal2007}, however, found that fairly thin He layers
could flash on sub-Chandrasekhar
mass white dwarfs, partially resolving the issue and encouraging
further research~\citep{simetal2012,brooksetal2015, shenetal2018,
glasneretal2018}.

The white dwarf merger progentor picture has two white dwarfs coming 
together and subsequently exploding~\citep{tutukovyungelson76,tutukovyungelson79,
webbink84,ibentutukov84}. This scenario provides an abundance of degenerate fuel, 
which may explain some bright events~\citep{scalzo:2010,Yuan:2010}. 
An early concern about this model came from studies finding that
the white dwarf will ignite at the edge and the coalesced object, 
and a flame will burn inward, converting the C-O white dwarf into 
an O-Ne-Mg white dwarf~\citep{saionomoto1985,saionomoto2004}, with
further accretion leading to the collapse of the white dwarf
into a neutron star, a scenario termed ``accretion-induced collapse''
\citep{nomotokondo1991}.

Subsequent work allayed this concern~\citep{yoonetal2007,lorenaguilaretal2009,
Shenetal12, pakmoretal2012b} and motivated by the need to expain briht events
and the estimated population WD pairs, active research continues. Contemporary
research focuses on variations on the merger idea, including 
inspiraling pairs, collisions, violent mergers,
and the ``core-degenerate'' model in which the merger takes place in
a common envelope \citep{raskinetal2009,pakmoretal2011,kashi:2011,pakmoretal2012a,Shenetal12,katzetal2016}.

@@

@@

\subsection{A Recent Advance in Stellar Evolution: Hybrid White Dwarfs}

\section{Methods}

@@

\subsection{Initial Conditions}
